### 2013-05-03 doc/dissertation/document/backmatter/spn_spatial_discretization.tex
adding cartesian mesh cell figure

\chapter{Finite Volume Discretization for the $SP_N$ Equations}
\label{chap:spn_spatial_discretization}
Finite volume discretization for the $SP_N$ equations.

>>>>

\chapter{Finite Volume Discretization for the $SP_N$ Equations}
\label{chap:spn_spatial_discretization}
The moment-discretized form of the $SP_N$ equations given by
Eq~(\ref{eq:spn_matrix}) for the monoenergetic case has yet to have
the spatial components of the solution and the derivative operators
discretized. To achieve this, we choose a conservation law approach,
using Eq~(\ref{eq:spn_matrix}) as the balance equation, to yield a
finite volume calculation \citep{leveque_finite_2002}. To do this, we
first define a control volume about point $(i,j,k)$ in the domain as a
cell in a Cartesian mesh as shown in Figure~\ref{fig:mesh_cell}).
\begin{figure}[h!]
  \begin{center}
    \scalebox{1.5}{
    \input{backmatter/mesh_cell.pdftex_t} }
  \end{center}
  \caption{\textbf{Cartesian mesh cell used for the spatial
      discretization of the $SP_N$ equations.} \textit{The cell is
      centered about $(i,j,k)$.}}
  \label{fig:mesh_cell}
\end{figure}
